\documentclass[14pt]{article}

\usepackage{fancyhdr}
\usepackage{extramarks}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage[plain]{algorithm}
\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage{relsize}
\usepackage{scrextend}

\usetikzlibrary{automata,positioning}

%
% Basic Document Settings
%

\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in

\linespread{1.1}

\pagestyle{fancy}
\lhead{\hmwkAuthorName}
\chead{\hmwkClass\ (\hmwkClassInstructor): \hmwkTitle}
\rhead{\firstxmark}
\lfoot{\lastxmark}
\cfoot{\thepage}

\renewcommand\headrulewidth{0.4pt}
\renewcommand\footrulewidth{0.4pt}

\setlength\parindent{0pt}

%
% Create Problem Sections
%

\newcommand{\enterProblemHeader}[1]{
    \nobreak\extramarks{}{Problem \arabic{#1} continued on next page\ldots}\nobreak{}
    \nobreak\extramarks{Problem \arabic{#1} (continued)}{Problem \arabic{#1} continued on next page\ldots}\nobreak{}
}

\newcommand{\exitProblemHeader}[1]{
    \nobreak\extramarks{Problem \arabic{#1} (continued)}{Problem \arabic{#1} continued on next page\ldots}\nobreak{}
    \stepcounter{#1}
    \nobreak\extramarks{Problem \arabic{#1}}{}\nobreak{}
}

\setcounter{secnumdepth}{0}
\newcounter{partCounter}
\newcounter{homeworkProblemCounter}
\setcounter{homeworkProblemCounter}{1}
\nobreak\extramarks{Problem \arabic{homeworkProblemCounter}}{}\nobreak{}

%
% Homework Problem Environment
%
% This environment takes an optional argument. When given, it will adjust the
% problem counter. This is useful for when the problems given for your
% assignment aren't sequential. See the last 3 problems of this template for an
% example.
%
\newenvironment{homeworkProblem}[1][-1]{
    \ifnum#1>0
        \setcounter{homeworkProblemCounter}{#1}
    \fi
    \section{Problem \arabic{homeworkProblemCounter}}
    \setcounter{partCounter}{1}
    \enterProblemHeader{homeworkProblemCounter}
}{
    \exitProblemHeader{homeworkProblemCounter}
}

%
% Homework Details
%   - Title
%   - Due date
%   - Class
%   - Section/Time
%   - Instructor
%   - Author
%


\newcommand{\hmwkClass}{CS 219}
\newcommand{\hmwkTitle}{Homework\ \#2}
\newcommand{\hmwkDueDate}{September 14, 2016}
\newcommand{\hmwkDueTime}{4:00pm}
\newcommand{\hmwkClassInstructor}{Dr. Egbert}
\newcommand{\hmwkAuthorName}{Matthew J. Berger}

%
% Title Page
%

\title{
    \vspace{2in}
    \textmd{\textbf{\hmwkClass:\ \hmwkTitle}}\\
    \normalsize\vspace{0.1in}\small{Due\ on\ \hmwkDueDate\ at \hmwkDueTime}\\
    \vspace{0.1in}\large{\textit{\hmwkClassInstructor}}
    \vspace{3in}
}

\author{\textbf{\hmwkAuthorName}}
\date{}

\renewcommand{\part}[1]{\textbf{\large Part \Alph{partCounter}}\stepcounter{partCounter}\\}

%
% Various Helper Commands
%

% Useful for algorithms
\newcommand{\alg}[1]{\textsc{\bfseries \footnotesize #1}}

% Alias for the Solution section header
\newcommand{\solution}{\textbf{\large Solution}}

% Alias for answers
\newcommand{\answer}{\textbf{\large Answer: }}

\begin{document}

\maketitle

\pagebreak

\begin{homeworkProblem}
	\large{\underline{Review Questions: }\\\small(All answers are from the slides provided for the course)}
	\begin{itemize}
		\item[1.1.)] What, in general terms, is the distinction between computer organization and computer architecture? \\
		\answer \underline{Computer organization} refers to the way a given instruction set is implemented in a particular processor. \underline{Computer Architecture} refers to the attributes of a system visible to the programmer. This is more analagous to an \underline{interface} while the organization describes the \underline{implementation}.
		\item[1.2.)] What, in general terms, is the distinction between computer structure and computer function? \\		
		\answer \underline{Computer structure} refers to the way in which componenets relate to each other, while \underline{Computer function} refers to the operation of individual components as part of the structure.
		\item[1.3.)] What are the four main functions of a computer? \\
		\answer
		\begin{enumerate}[label=\arabic*.)]
			\item \underline{Data Processing}
				\begin{enumerate}[label=\alph*.)]
					\item Data may take a wide variety of forms and the range of processing requirements is broad.
				\end{enumerate}
			\item \underline{Data Storage}
				\begin{enumerate}[label=\alph*.)]
					\item Short-term
					\item Long-term
				\end{enumerate}
			\item \underline{Data Movement}
				\begin{enumerate}[label=\alph*.)]
					\item Input-Output (I/O) - When data is received from or delivered to a device (peripheral) that is directly connected to the computer.
					\item Data Communications - When data is moved
				\end{enumerate}
			\item \underline{Control}
				\begin{enumerate}[label=\alph*.)]
					\item A control unit manages the computer's resources and orchestrates the performance of its functional parts in response to instructions.
				\end{enumerate}
			\end{enumerate}
			\pagebreak
			\item[1.4.)] List and briefly define the main structural components of a computer. \\
			\answer There are four main structural components of the computer:
				\begin{enumerate}
					\item \underline{CPU} - Controls the operation of the computer and performs its data processing functions.
					\item \underline{Main Memory} - Stores Data
					\item \underline{I/O} - Moves data between the computer and its external environment.
					\item \underline{Sytem Interconnection} - Some mechanism that provides for communication among CPU, main memory, and I/O.

				\end{enumerate}
			\item[1.5.)] List and briefly define the main structural components of a processor. \\
			\answer There are four main structural components of a CPU:
			\begin{enumerate}
				\item \underline{Control Unit} - Controls the operation of the CPU and hence the computer.
				\item \underline{Arithmetic Logic Unit} - Performs the computer's data processing function.
				\item \underline{Registers} - Provide storage internal to the CPU.
				\item \underline{CPU Interconnection} - Some mechanism that provides for communication among the control unit, ALU, and registers.
			\end{enumerate}
		
		\item[1.6.)] What is a stored program computer? \\
		\answer A stored program computer is one that stores program instructions in memory.
		\item[1.7.)] Explain Moore's law. \\
		\answer Moore's law was an observation made in 1965 that the \underline{number of transistors} per square inch on integrated circuits \underline{was doubling each year} since its inception. Gordon Moore (co-founder of Intel) predicted that this would continue to happen ad-infinitum.
		\item[1.8.)] List and explain the key characteristics of a computer family. \\
		\answer
			\begin{enumerate}[label=\alph*.)]	
			\item Similar or identical instruction set
			\item Similar or identical operating system
			\item Increasing speed
			\item Increasing number of I/O ports
			\item Increasing memory size
			\item Increasing cost
			\end{enumerate}
		\item[1.9.)] What is the key distinguishing feature of a microprocessor? \\
		\answer The key distinguishing feature of a microprocessor is that it is a combination of many different circuits integrated into a single chip to provide highly complex functionality.
	\end{itemize}
\end{homeworkProblem}

\pagebreak

\begin{homeworkProblem}
	\large{\underline{Problems:}}
	\begin{itemize}
		\item[2.1)] You are to write an IAS program to compute the results of the following equation.
		\item[] \(\hfil Y = \sum_{X=1}^{N}X\)
		\item[] Assume that the computation does not result in an arithmetic overflow and that X, Y, and N are positive integers with $N \geq 1$.		
		Note: Even though the IAS did not have assembly language, only machine language, you will use the assembly language show in the text for this program.
		\begin{enumerate}[label=\alph*.)]
			\item Use the equation $Sum(Y) = \frac{(N(N+1))}{2}$ when writing the IAS program.
			\item Do it the "hard way", without using the equation from part (a).
		\end{enumerate}
	\end{itemize}	
	
	\solution
	
	\textbf{Part A}
	
	\begin{table}[h]
		\def\arraystretch{1.5}%
		\begin{tabular}{|l|l|l|}
			\hline
			\multicolumn{1}{|c|}{Location} & \multicolumn{1}{|c|}{Instruction} & \multicolumn{1}{|c|}{Comments} \\
			\hline
			0  & (value)           & Constant N initialized to some value  \\
			1  & 1                 & Constant integer value = 1 \\
			2  & 2                 & Constant integer value = 2 \\
			3  & 0                 & Variable Y = Sum (initialized to 0)  \\			
			4L & LOAD M(0)         & $AC \leftarrow N$ \\
			4R & ADD M(1)          & $AC \leftarrow AC + 1 $ \\
			5L & MUL M(0)          & $AC \leftarrow N(N+1)$ \\
			5R & DIV M(2)          & $AC \leftarrow \frac{AC}{2}$ \\
			6L & STOR M(3)         & $Y \leftarrow AC$ (Save the accumulated sum in variable Y)\\
			6R & JUMP M(6,20:39)   & Done. HALT \\				
			\hline
		\end{tabular}
	\end{table}
	
	\pagebreak
	
	\textbf{Part B}
	
	\begin{table}[h]
		\def\arraystretch{1.5}%
		\begin{tabular}{|l|l|l|}
			\hline
			\multicolumn{1}{|c|}{Location} & \multicolumn{1}{|c|}{Instruction} & \multicolumn{1}{|c|}{Comments} \\
			\hline
			0  & (value)           & Constant N initialized to some value  \\ 
			1  & 1                 & Increment step size \\
			2  & 1                 & Current index \\
			3  & 1                 & Variable Y = Sum (initialized to 1)  \\			
			4L & LOAD M(0)         & $AC \leftarrow N$ \\
			4R & SUB M(2)          & $AC \leftarrow N - i $ \\
			5L & JUMP + M(6,0:19)  & Check $AC \geq 0$ \\
			5R & JUMP + M(5,20:39) & $i=N$ Done. HALT \\
			6L & LOAD M(2)         & $i<N$ so continue by retrieving the current index \\
			6R & ADD M(1)          & $AC \leftarrow i + 1 $ \\
			7L & STOR M(2)         & $AC \rightarrow i$ \\
			7R & ADD M(3)          & $AC \leftarrow i + Y$ \\
			8L & STOR M(3)         & $AC \rightarrow Y$ \\
			8R & JUMP M(4,0:19)    & Jump to instruction located at 4L \\						
			\hline
		\end{tabular}
	\end{table}
\end{homeworkProblem}

\pagebreak

\end{document}
